Active-contours driven registration method for structure-informed segmentation of diffusion MR images

### 2015-04-13 Publications/2015-NeuroImage/03-introduction.tex
minor fixes

% -*- root: 00-main.tex -*-
\section{Introduction}\label{sec:introduction}
The accurate delineation of \gls*{wm} in \gls*{dmri} and the fusion of prior
  anatomical information extracted from a \gls*{t1} image of the same subject
  are crucial in a range of applications based on tractography, such as
  the extraction of structural connectivity \citep{craddock_imaging_2013} or
  tract-based spatial statistics \citep{smith_tractbased_2006}.
However, segmenting \gls*{dmri} data precisely and coregistration of anatomical
  images are difficult due to several limitations.
First, \gls{dmri} images suffer from partial voluming of several tissues in 
  voxels located at their interfaces due to the low resolution of images
  (generally around \isores[mm]{2.2}).
Second, \gls*{dmri} schemes probe the diffusion process within the brain in 
  many angles called \glspl*{dwi}, completed by one or more baseline (\emph{b0}) 
  volumes without directional gradients.
The extremely low \gls*{snr} and high dimensionality of \glspl*{dwi} disable their
  direct use in segmentation.
The low contrast between \gls*{gm} and \gls*{wm} in the \emph{b0} volumes is not suitable for 
  segmentation either.
Lastly, \gls*{dmri} images are acquired using \gls*{epi} to speed up acquisition
  at the cost of introducing geometrical distortion and signal degradation and
  destruction \citep{jezzard_correction_1995}.
The artifact has been proven to cause an important impact on the anatomy extracted
  from \gls*{dmri} \citep{irfanoglu_effects_2012}, particularly in certain fiber bundles
  when used in whole-brain tractography.
These limitations preclude segmentation in native \gls*{dmri} space, including
  registration-based approaches using anatomical images as source of structural
  information.

>>>>

% -*- root: 00-main.tex -*-
\section{Introduction}\label{sec:introduction}
The accurate delineation of \gls*{wm} in \gls*{dmri} and the fusion of prior
  anatomical information extracted from a \gls*{t1} image of the same subject
  are crucial in a range of applications based on tractography, such as
  the extraction of structural connectivity \citep{craddock_imaging_2013} or
  tract-based spatial statistics \citep{smith_tractbased_2006}.
However, segmenting \gls*{dmri} data precisely, and coregistration of anatomical
  images are difficult due to several limitations.
First, \gls{dmri} images suffer from partial voluming of several tissues in 
  voxels located at their interfaces due to the low resolution of images
  (generally around \isores[mm]{2.2}).
Second, \gls*{dmri} schemes probe the diffusion process within the brain in 
  many angles called \glspl*{dwi}, completed by one or more baseline (\emph{b0}) 
  volumes without directional gradients.
The extremely low \gls*{snr} and high dimensionality of \glspl*{dwi} disable their
  direct use in segmentation.
The low contrast between \gls*{gm} and \gls*{wm} in the \emph{b0} volumes is not suitable for 
  segmentation either.
Lastly, \gls*{dmri} images are acquired using \gls*{epi} to speed up acquisition
  at the cost of introducing geometrical distortion and signal degradation and
  destruction \citep{jezzard_correction_1995}.
The artifact has been proven to cause an important impact on the anatomy extracted
  from \gls*{dmri}, particularly in certain fiber bundles \citep{irfanoglu_effects_2012}.
These limitations preclude segmentation in native \gls*{dmri} space, including
  registration-based approaches using anatomical images as source of structural
  information.
